---
title: "Linear regression using the gradient descent method"
author:
  - name: "Carlos Olivos ^[Email: cro0010@auburn.edu]"
  - name: "Ridvan Ozdemir ^[Email: rzo0012@auburn.edu]"
  - name: "Ogonnaya Romanus ^[Email: omr0010@auburn.edu]"
output: html_document
---
# FinalProject_Group7/group7project

This project is an R package to fit a linear model for a given data using the gradient descent method. The user must provide a matrix that corresponds to the predictors and the response variable from the dataset, which must be a vector with the same length as the matrix length. Moreover, the significance level for the regression 
coefficients' confidence intervals, alpha, must be between 0 and 1. 
The gradient descent method requires the learning rate, which must be between 0 and 1. Also, this method requires a number of iterations, which has to be a positive integer. Thus, the higher the learning rate, the faster convergence will occur. Moreover, with more iterations, the model will provide a better estimation for the regression coefficients. Nevertheless, the above will increase the computational time. The default values of the above parameters are as follow:  `alpha=0.05`, `learning rate =0.1` and `iteration=1000`.

```{r eval=FALSE}
lin_reg(response, predictor, alpha = 0.05, learning_rate = 0.1, iterations = 1000)
```

The function has two different outputs. The first one is a list of tables: 
```{r eval=FALSE}
list(table_betas, tab_ci, tab_R_sq, tab_C_p, tab_F_star, tab_p)
```
with `table_betas` the vector of coefficient whose length is the same as `response` such that `response = predictor%*%betas`

* **tab_ci:** the table with the confidence intervals for `Beta`

* **tab_R_sq:** R-square value

* **tab_C_p:** $C_p$ value

* **tab_F_star:** $F^{\star}$ value

* **tab_p:** p-value

The second output are plots where

* **Plot1:** the plot of Residual vs Fitted-values
* **Plot2:** the qq-plot of Residuals
* **Plot3:** Histogram of Residuals

## Example
The function `lin_reg` is applied to Dataset `abalone.data` as follows

```{r message=FALSE, warning=FALSE}
devtools::install_github("AU-R-Programming/FinalProject_Group7/group7project")
library(group7project)
abalone <- read.csv(file = 'abalone.csv')
abalone = subset(abalone, select = -Sex)
y <- abalone$Rings
x = abalone
x <- subset(x, select = -Rings)
lin_reg(response = y,predictor = x,alpha = 0.05,learning_rate = 0.1,iterations = 10000)
```








