---
title: "vignette"
output: html_document
---
# FinalProject_Group7/group7project

This project is a R package to fit a linear model for a given data using gradient decent method. The user must provide an explanatory data which must be a matrix and a response data which must be a vector whose length is the same with the number of rows of the explanatory data. Also, deciding alpha value for confidence interval which must be less than 1, learning rate for gradient decent method and number of iterations of gradient decent method are possible but not compulsory. They are `alpha=0.05`, `learning rate =0.1` and `iteration=1000` by default.

```{r eval=FALSE}
lin_reg(response, predictor, alpha = 0.05, learning_rate = 0.1, iterations = 1000)
```

The function has two different outputs. The first one is a list of tables: 
```{r eval=FALSE}
list(table_betas, tab_ci, tab_R_sq, tab_C_p, tab_F_star, tab_p)
```
with 
\arguments
\item{table_betas} the vector of coefficient whose length is the same as `response` such that `response = predictor%*%betas`

\item{}* **tab_ci** the table of confidence intervals for `Beta`

\item{}* **tab_R_sq** R-square value

* **tab_C_p** $C_p$ value

* **tab_F_star** $F^{\star}$ value

* **tab_p** p-value

The second output is plots where

* **Plot1** the plot of Residual vs fitted-values
* **Plot2** the qq-plot of Residuals
* **Plot3** Histogram of Residuals

## Example
The function `lin_reg` is applied to Dataset `abalone.data` as follows

```{r message=FALSE, warning=FALSE}
devtools::install_github("AU-R-Programming/FinalProject_Group7/group7project")
library(group7project)
abalone <- read.csv(file = 'abalone.csv')
abalone = subset(abalone, select = -Sex)
y <- abalone$Rings
x = abalone
x <- subset(x, select = -Rings)
lin_reg(response = y,predictor = x,alpha = 0.05,learning_rate = 0.1,iterations = 10000)
```








