---
title: "Linear_Regression_Via_Gradient_Descent"
author:
  - name: "Carlos Olivos ^[Email: cro0010@auburn.edu]"
  - name: "Ridvan Ozdemir ^[Email: rzo0012@auburn.edu]"
  - name: "Ogonnaya Romanus ^[Email: omr0010@auburn.edu]"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear_Regression_Via_Gradient_Descent}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


**Github Repository Name and Page:**  [FinalProject_Group7]( https://au-r-programming.github.io/FinalProject_Group7/)




In this project, an R package to fit a linear regression model for a given data using the gradient descent method is built. To use this package, the user must provide a matrix/data frame whose columns corresponds to the predictors; and a response variable, which must be a vector with the same length as the number of rows of the matrix/data frame. Moreover, the significance level for the regression coefficients' confidence intervals, alpha, must be between 0 and 1.

The gradient descent method requires the learning rate, which must be between 0 and 1. Also, this method requires the user to provide a number of iterations, which has to be a positive integer. Thus, the higher the learning rate, the faster convergence will occur. Moreover, with more iterations, the model will provide a better estimation for the regression coefficients. Nevertheless, the above will increase the computational time. The default values of the above parameters are as follow:  `alpha=0.05`, `learning rate =0.1` and `iteration=1000`.

The package can be install directly from Github.

```{r, warning=FALSE, message=FALSE}
devtools::install_github("AU-R-Programming/FinalProject_Group7/group7project")
```


The implementation of the package uses the `lin_reg()` function.

```{r eval=FALSE}
lin_reg(response, predictor, alpha = 0.05, learning_rate = 0.1, iterations = 1000)
```


The function returns two sets of outputs.

 The first is a list of tables: 
```{r eval=FALSE}
list(table_betas, tab_ci, tab_R_sq, tab_C_p, tab_F_star, tab_p)
```

* **table_betas:** a vector of estimated linear regression coefficients `betas`

* **tab_ci:** the table with the confidence intervals for `betas`

* **tab_R_sq:** R-square value

* **tab_C_p:** $C_p$ value

* **tab_F_star:** $F^{\star}$ value

* **tab_p:** p-value

The second outputs are plots:

* **Plot1:** the plot of Residual vs Fitted-values
* **Plot2:** the qq-plot of Residuals
* **Plot3:** Histogram of Residuals


## Example
As an illustration, we utilize the package to perform linear regression on the data set `abalone.data`, provided on the canvas of this course.

```{r message=FALSE, warning=FALSE}
library(group7project)
abalone <-read.csv("abalone.csv")
abalone = subset(abalone, select = -Sex)
y <- abalone$Rings
x = abalone
x <- subset(x, select = -Rings)
lin_reg(response = y,predictor = x,alpha = 0.05,learning_rate = 0.1,iterations = 10000)
```



